Data Specialization for a Staged Lambda Calculus

### 2015-02-02 paper/example.tex
edits all over (syntax) and masking section
small edits to the front

@@

We define a staged version of quickselect in \ref{fig:qs-staged}, writing
first-stage computations in red, and second-stage computations in blue. While
\texttt{qSelect} sends a \textrm{list} and \rmint\ to an \rmint,
\texttt{qsStaged} has a more precise type---it is a first-stage function which
takes a \textrm{list} and a $\fut\rmint$ (an $\rmint$ \emph{in the future}), and
returns a $\fut\rmint$.

\crem{Next three paragraphs are waiting on exact code for \ref{fig:qs-staged}.
Use three colors?}

@@

@@

In this paper, we develop a splitting algorithm
(\ref{sec:splitting,sec:implementation}) which, for any term $e$ in \lang,
produces a pair of terms $e_1,e_2$ containing respectively all the first- and
second-stage content of $e$, such that $e_2~e_1$ is equivalent to $e$.
(Such a splitting is always possible because $e$ is well-typed in \lang.) In the
case of \texttt{qsStaged}, our splitting algorithm produces the algorithm
described above.

>>>>

\begin{concretesyntax}

@@

We define a staged version of quickselect in \ref{fig:qs-staged}, writing
first-stage computations in red, and second-stage computations in blue. While
\texttt{qSelect} sends a \textrm{list} and \rmint\ to an \rmint,
\texttt{qsStaged} has a more precise type---it is a first-stage function which
takes a \textrm{list} (ignore the $\curr$ for now) and a 
$\fut\rmint$ (an $\rmint$ \emph{in the future}), and returns a $\fut\rmint$.

@@

The quickselect example also contains some {\em purity annotations}, 
$\curr$ and \texttt{@pure}, which indicate regions of code that are 
contain no stage \bbtwo\ code (i.e. they are purely stage \bbone),
which allow more efficient code generation down the line.

@@

In this paper, we develop a splitting algorithm
(\ref{sec:splitting,sec:implementation}) which, for any term $e$ in \lang,
produces an equivalent term where the stages of computation 
are syntactically seperated at the top level.
(Such a splitting is always possible because $e$ is well-typed in \lang.) In the
case of \texttt{qsStaged}, our splitting algorithm produces the algorithm
described above.
